### 2015-01-09 fundamentals/impl.tex
overuse of the word 'key'

A key innovation is that \Cyclus  implements this generic \gls{API} and modular 
architecture via a suite of dynamically loadable plug-in libraries.  Though 
common in modern software architecture, such a plug-in pattern has 
not previously been implemented in nuclear fuel cycle simulators.  
Dynamically loadable libraries are the primary mechanism for extending \Cyclus' capability. This approach provides encapsulation: the core of the code operates
completely independently from the individual plug-in libraries. Thus, any
customization or extension is implemented only in the loadable
library.

@@

\Cyclus implements an \acrlong{ABM} paradigm.  \gls{ABM} is modern, sophisticated, 
true to reality, and it incorporates modern computing resources.  
Furthermore, \gls{ABM} provides a natural 
perspective from which to model a given problem. In the nuclear fuel cycle 
context, for example, an analyst can design an agent with reactor-related logic 
that is entirely independent from an agent with fuel fabrication-related 
logic. Defining the behavior of both agents according to the 
\gls{API} contract is sufficient for them to interact with one another as 
bona fide actors in the simulation.  The two archetype libraries can be used in the same
simulation without any shared knowledge.

Furthermore, the \gls{ABM} paradigm is easily comparable to system dynamics models.
System dynamics is a popular approach for modeling nuclear fuel cycles 
\cite{jacobson_vision_2009,van_den_durpel_daness_2009,guerin_impact_2009,guerin_benchmark_2009}. 
Formally however, system dynamics models are simply a strict subset of agent-based models
\cite{macal_agent-based_2010}.
That is, any system dynamics model can be translated
into an agent-based model. Furthermore, because agent-based
techniques can provide a richer model than can system dynamics, they enable the 
broadest range of simulations in a generic fashion.

@@

\gls{ABM} is inherently object-oriented because agents represent 
discrete, independently acting objects.  Figure \ref{fig:framework} illustrates
the modular nature of \Cyclus archetypes.  The core of the \Cyclus simulator 
creates a set of key classes on which agent plug-ins 
are based. In addition, a set of key tools are also provided to enrich the 
\gls{API} and supply a robust suite of behaviors for the developer. 
Agent plug-ins utilize the generic core \gls{API} to interact with one another.  For 
example, agents rely on a paradigm of dynamic loading and clean plug-in 
behavior at the start of the simulation. They also use the resource exchange 
paradigm \gls{API} for trading resources with one another.

@@

The act of proposing a change is known as a \emph{pull request}. The main \Cyclus repository is 
hosted remotely on the GitHub website \cite{dabbish_social_2012}. The online
mechanism for pull requests allows for code review by a member of the \Cyclus 
core team, separate from the author, prior to any change being included. Non-members
of the \Cyclus development team are allowed and encouraged to submit and review 
pull requests. However, only members of the \Cyclus core team are allowed to 
merge in any changes and only after the \gls{QA} standards have been met.

>>>>

A key innovation is that \Cyclus  implements this generic \gls{API} and modular 
architecture via a suite of dynamically loadable plug-in libraries.  Though 
common in modern software architecture, such a plug-in pattern has 
not previously been implemented in nuclear fuel cycle simulators.  
Dynamically loadable libraries are the primary mechanism for extending \Cyclus' capability. This approach provides encapsulation: the core of the code operates
independently from the individual plug-in libraries. Thus, any
customization or extension is implemented only in the loadable
library.

@@

\Cyclus implements an \acrlong{ABM} paradigm.  \gls{ABM} is modern, sophisticated, 
true to reality, and incorporates modern computing resources.
Furthermore, \gls{ABM} provides a natural 
perspective from which to model a given problem. In the nuclear fuel cycle 
context, for example, an analyst can design an agent with reactor-related logic 
that is entirely independent from an agent with fuel fabrication-related 
logic. Defining the behavior of both agents according to the 
\gls{API} contract is sufficient for them to interact with one another as 
bona fide actors in the simulation.  The two archetype libraries can be used in the same
simulation without any shared knowledge.

Furthermore, the \gls{ABM} paradigm is superior to system dynamics used in 
current simulators.
System dynamics is a popular approach for modeling nuclear fuel cycles 
\cite{jacobson_vision_2009,van_den_durpel_daness_2009,guerin_impact_2009,guerin_benchmark_2009}. 
Formally however, system dynamics models are simply a strict subset of agent-based models
\cite{macal_agent-based_2010}.
That is, any system dynamics model can be translated
into an agent-based model. Furthermore, because agent-based
techniques can provide a richer model than can system dynamics, they enable the 
broadest range of simulations in a generic fashion.

@@

\gls{ABM} is inherently object-oriented because agents represent 
discrete, independently acting objects.  Figure \ref{fig:framework} illustrates
the modular nature of \Cyclus archetypes.  The core of the \Cyclus simulator 
creates a set of classes on which agent plug-ins 
are based. In addition, a set of tools are also provided to enrich the 
\gls{API} and supply a robust suite of behaviors for the developer. 
Agent plug-ins utilize the generic core \gls{API} to interact with one another.  For 
example, agents rely on a paradigm of dynamic loading and clean plug-in 
behavior at the start of the simulation. They also use the resource exchange 
paradigm \gls{API} for trading resources with one another.

@@

The act of proposing a change is known as a \emph{pull request}. The main \Cyclus repository is 
hosted remotely on the GitHub website \cite{dabbish_social_2012}. The online
mechanism for pull requests allows for code review by a member of the \Cyclus 
core team, separate from the author, prior to any change being included. Non-members
of the \Cyclus development team are allowed and encouraged to submit and review 
pull requests. However, only members of the \Cyclus core team are allowed to 
merge in any changes and only after the \gls{QA} standards have been met. This 
step has been repeatedly shown to improve code quality \cite{cohen_modern_2010}.
